%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Filename    : references.tex 
%
%   Description : This file will contain your list of references.
%                 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{References}
\label{sec:References}

\sloppy
\begin{adjustwidth}{0.1in}{0.1in}
Alzheimer's Research UK. (2020, March 13). Sea Hero Quest. Retrieved from https://www.alzheimersresearchuk.org/research/for-researchers/resources-and-information/sea-hero-quest/. 

American Physical Society. (October 2008). October 1958: Physicist Invents First Video Game. Retrieved from https://www.aps.org/publications/apsnews/200810/physicshistory.cfm

Bergonse, R. (2017). Fifty Years on, What exactly is a video game? An essentialistic definitional approach. The Computer Games Journal,6(4), 239–255. Retrieved from
https://doi.org/10.1007/s40869-017-0045-4

Colorado College. (2020). Bloom’s Revised Taxonomy. Retrieved from https://www.coloradocollege.edu/other/assessment/how-to-assess-learning/learning-outcomes/blooms-revised-taxonomy.html

Counter-Strike: Global Offensive. [Video game]. (2012). Valve Corporation

Department of Education. (2019). K to 12 Basic Education Curriculum Senior High School - Science, Technology, Engineering and Mathematics (STEM) Specialized Subject Retrieved from https://www.deped.gov.ph/wp-content/uploads/2019/01/Pre-Calculus.pdf

Department of Education. (2018). PISA 2018 National Report of the Philippines. Retrieved from https://www.deped.gov.ph/wp-content/uploads/2019/12/PISA-2018-Philippine-National-Report.pdf.

DOTA 2. [Video game]. (2013). Valve Corporation 


Erik Hazzard (2020, November 5). Data Visualization in games. GameAnalytics. Retrieved from https://gameanalytics.com/blog/data-visualization-games/. 

Gamelearn. (2020, November 13). Serious games examples that explain all you need to know. Retrieved from https://www.game-learn.com/all-you-need-to-know-serious-games-game-based-learning-examples/. 

Gleim Aviation. (2021). X-Plane Flight Training Course. Retrieved from https://www.gleimaviation.com/xplane/

Jaudinez, A. S. (2019). Teaching Senior High School Mathematics: Problems and Interventions. Pedagogical Research, 4(2), em0031. Retrieved from 
https://doi.org/10.29333/pr/5779

Kamnardsiri, T., Hongsit, L.-on, Khuwuthyakorn, P., Wongta, N. (2017). The Effectiveness of the Game-Based Learning System for the Improvement of American Sign Language using Kinect. Retrieved from https://files.eric.ed.gov/fulltext/EJ1154946.pdf. 

Kauffmann, Archava, Castles, Ries, Sullivan, Urquidi, P. S. R. H. S. K. (2011). FACTORS IMPACTING POOR PERFORMANCE IN PRE CALCULUS. Retrieved from https://www.asee.org/file\_server/papers/attachment/file/0001/0803/Pre\_calculus \\ \_ASEE\_2011\_021611.pdfroolvink

Laamarti, F., Eid, M., El Saddik, A. (2014, October 15). An Overview of Serious Games. International Journal of Computer Games Technology. Retrieved from https://www.hindawi.com/journals/ijcgt/2014/358152/

League of Legends (PC version) [Video game]. (2013). Riot Games Inc.

Litts, B., Ramirez, D. (2014). Making people fail: Failing to learn through games and making. Proceedings GLS, 10(2014), 160-166.

Magsambol, B. (2020, December 12). PH lowest among 58 countries in math, science – global assessment. Rappler. Retrieved from https://www.rappler.com/nation/filipino-students-lagging-behind-math-science-timms-international-results-2019. 

Mestadi, W. (2018). An Assessment of Serious Games Technology: Toward an Architecture for Serious Games Design. Retrieved from https://www.hindawi.com/journals/ijcgt/2018/9834565/

Organization for Economic Co-operation and Development. (2018). Programme For International Student Assessment (PISA) Results From PISA 2018. Retrieved from https://www.oecd.org/pisa/publications/PISA2018\_CN\_PHL.pdf.

Plass, J., Homer, B., Kinzer, C. (2015). Foundations of Game-Based Learning. Retrieved from https://files.eric.ed.gov/fulltext/EJ1090277.pdf

Rebbah, H.B.. (2019). The educational effectiveness of serious games. Retrieved from \burl{https://www.researchgate.net/publication/337367093\_The\_educational\_effectiveness\_of\_serious\_games}

Roolvink, F. (2021, March 18). What are serious games? Grendel Games. Retrieved from https://grendelgames.com/what-are-serious-games/

Schoenau-Fog, H. (2011). The Player Engagement Process - An Exploration of Continuation Desire in Digital Games. Retrieved from  http://digra.org/wp-content/uploads/digital-library/11307.06025.pdf

Sharek, D. (2018, September 12). The importance of player engagement. Medium. Retrieved from https://medium.com/horizonperformance/the-importance-of-player-engagement-e424bddc9e87. 

Shute, V., Ke, F.. (2012). Games, Learning, and Assessment. Retrieved from https://www.researchgate.net/publication/283395597\_Games\_Learning\_ \\ and\_Assessment

Sison, R.C., Espulgar, C., Madrigal, L., OBEDOZA, J.B., ROMBLON, N. (2018). Toward an Outcome-Based Methodology for Developing Game-Based Learning Environments. Retrieved from http://icce2018.ateneo.edu/wp-content/uploads/2018/12/C5-11.pdf

Stiller, K. D., Schworm, S. (2019, February 19). Game-Based Learning of the Structure and Functioning of Body Cells in a Foreign Language: Effects on Motivation, Cognitive Load, and Performance.  Retrieved from https://www.frontiersin.org/articles/10.3389/feduc.2019.00018/full\#h4.

Valorant (PC version) [Video game]. (2020). Riot Games Inc.

World Without Oil. (n.d.). Learn About :: World Without Oil. Retrieved from http://writerguy.com/wwo/metaabout.htm. 

Zammitto, V. (2008). Visualization Techniques in Video Games. Retrieved from http://www.sfu.ca/~vzammitt/papers/zammitto-EVA-Visualization\_Techniques\_in\_VideoGames.pdf
\end{adjustwidth}
\fussy